---
title: "BOO2024 - Hands-on workshop DEG analysis"
author: "Imke Bruns (MSc), Steven Kunnen (PhD), Giulia Callegaro (PhD), Hugo van Kessel (Msc)"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    theme: default
    highlight: kate
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

# Setup {.tabset}
```{r include=FALSE, echo=TRUE, message=FALSE}
rm(list = ls()); gc()
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 80), tidy = TRUE)
```

## Load packages
### Bioconductor
```{r}
# Check if BiocManager is available and install
if(!require("BiocManager", quietly = T)){install.packages("BiocManager")}; library(BiocManager)

# Check if BiocManager is available and install
if(!require("DESeq2", quietly = T)){BiocManager::install("DESeq2", force = TRUE)}; library(DESeq2)
```

### CRAN
```{r}
# Check if pacman is available and install
if(!require("pacman", quietly = T)){install.packages("pacman")}; library(pacman)

# use packman to install CRAN packages
p_load(tidyverse, ggpubr, data.table, ggfortify, stats)
```

## Set directories
```{r}
# input directory
if(!dir.exists("INPUT")){
  dir.create(path = file.path(getwd(), "INPUT"))
}
input_dir <- file.path(getwd(), "INPUT")

# output directory
if(!dir.exists("OUTPUT")){
  dir.create(path = file.path(getwd(), "OUTPUT"))
}
output_dir <- file.path(getwd(), "OUTPUT")
```

## Load functions
```{r}

# Function: tidy check deseq input  ----
tidy_check = function(countdata, metadata) {
  # We assume first column will contain the row names (tidy = T in DESeqDataSetFromMatrix)
  names_count = names(countdata)[-1]
  # Not obligatory for DEseq2, but we want row names in the first column
  names_meta = metadata[[1]]
  # Test if the names from the count and metadata are identical (same entries, same order)
  identical = identical(names_count, names_meta)
  # If not identical, do we have the same entries (ignores duplicates)
  setequal = identical || setequal(names_count, names_meta)
  # Test for duplicates (in theory, but very unlikely, this can also happen if identical is true)
  has_duplicates = anyDuplicated(names_meta) > 0
  # If the names are not identical, but we're looking at the same entries without duplicates,
  # then the problem is the order of the entries
  problem_is_order = !identical && setequal && !has_duplicates
  # List possibilities to test
  input = list(identical = identical, setequal = setequal, has_duplicates = has_duplicates, problem_is_order = problem_is_order)

  if(input$identical & input$setequal & !input$has_duplicates & !input$problem_is_order){
    return(TRUE)
  } else {
    print(input)
    return(FALSE)
  }
}
```

# Load data {.tabset}
## Metadata
```{r}
metadata = fread(file.path(input_dir, "20240603filtered_metadata_processed_human.csv"))
```

## Raw counts
```{r}
countdata_raw = fread(file.path(input_dir, "20240603filtered_countdata_raw_processed_human.csv"))
```

# Differential gene expression analysis based on the negative binomial distribution (DESeq2 package) {.tabset}
## Generate contrast
### Set control condition
```{r error=F,warning=F,message=F, echo=F}
control_condition =  c("DMSO")
```

### Create the `contrast_table`
```{r error=F,warning=F,message=F, echo=F}
# We generate a contrast table which contains the mean_id comparison we aim the perform
contrast_control = metadata %>%
  filter(COMPOUND %in% control_condition) %>%
  distinct(MEAN_ID, TIME, COMPOUND)


contrast_treatment = metadata %>%
  filter(!COMPOUND %in% control_condition) %>%
  distinct(MEAN_ID, TIME, COMPOUND)


contrast_table = left_join(x = contrast_treatment %>%
                             select(MEAN_ID_TREATMENT = MEAN_ID, TIME, EXPERIMENT = COMPOUND),
                           y = contrast_control %>%
                             select(MEAN_ID_CONTROL = MEAN_ID, TIME, CONTROL = COMPOUND),
                           by = "TIME") %>%
  distinct()


contrast_table %>%
  select(MEAN_ID_TREATMENT, MEAN_ID_CONTROL) %>%
  as_tibble() %>%
  print(n = 1000)
```

## Run DESeq2
```{r error=F,warning=F,message=F, echo=F}

# We set the thresholds to find differential expressed genes
padj_threshold <- 0.05
log2FC_threshold <- log2(1.5)

# We loop over the contrast table and select the corresponding data, make the DESeq object, cpm normalize, contrast the treatment with the control and print the ouput
deseq_results = tibble()


  if(nrow(metadata)==ncol(countdata_raw)-1){
    
    if(tidy_check(countdata = countdata_raw, metadata = metadata)){
      deseq_object = DESeqDataSetFromMatrix(countData =  as.data.frame(countdata_raw),
                                                 colData = metadata %>% mutate(MEAN_ID = as.factor(MEAN_ID)),
                                                 design = ~ MEAN_ID + REPLICATE,
                                                 tidy = TRUE)
    }
    sizeFactors(deseq_object) = colSums(column_to_rownames(countdata_raw, var = "GENE_SYMBOL"))/1E6
    deseq_object = DESeq(deseq_object)

    for(i in 1:nrow(contrast_table)){
    temp = data.frame(
      results(deseq_object, contrast = c("MEAN_ID", contrast_table$MEAN_ID_TREATMENT[i], contrast_table$MEAN_ID_CONTROL[i]))) %>%
      rownames_to_column(var = "gene_symbol") %>%
      mutate(MEAN_ID_TREATMENT = contrast_table$MEAN_ID_TREATMENT[i], 
             MEAN_ID_CONTROL = contrast_table$MEAN_ID_CONTROL[i]) %>% tibble()
    
    
    up = temp %>% filter(padj < padj_threshold & log2FoldChange >= log2FC_threshold) %>% nrow()
    down = temp %>% filter(padj < padj_threshold & log2FoldChange <= -log2FC_threshold) %>% nrow()
    
    cat(
      paste("Treatment", contrast_table$MEAN_ID_TREATMENT[i], "vs. control", contrast_table$MEAN_ID_CONTROL[i]), 
      "\npadj threshold =", padj_threshold, "log2FC threshold =", log2FC_threshold, 
      "\nUp regulated DEGs =", up, "\nDown regulated DEGs =", down)
    cat("\n")
    cat("\n")
    
    deseq_results = deseq_results %>% bind_rows(temp)
  }
}

# We print the DESeq result table
{
  cat("\n")
  print("DESeq2 output table")
  cat("\n")
  deseq_results %>% str()  
}
```

# Inspect DESeq2 output {.tabset}
## Log2FC vs FC
```{r error=F,warning=F,message=F}
# We plot a density plot using the foldchange values of the treatment conditions
deseq_results %>% 
  select(log2FoldChange, MEAN_ID_TREATMENT) %>% 
  mutate(FoldChange = 2^log2FoldChange) %>% 
  ggplot() +
  geom_density(mapping = aes(x = FoldChange)) +
  facet_wrap(~MEAN_ID_TREATMENT) +
  theme_bw() + 
  labs(title = "Density plot of FoldChange values")

# We ZOOM on x = c(0,10) and plot a density plot using the foldchange values of the treatment conditions
deseq_results %>% 
  select(log2FoldChange, MEAN_ID_TREATMENT) %>% 
  mutate(FoldChange = 2^log2FoldChange) %>% 
  ggplot() +
  geom_density(mapping = aes(x = FoldChange)) +
  facet_wrap(~MEAN_ID_TREATMENT) +
  theme_bw() + 
  labs(title = "ZOOM on x = c(0,10) Density plot of FoldChange values") +
  coord_cartesian(xlim = c(0,10)) +
  scale_x_continuous(breaks = 0:10)

# We plot a density plot using the log2foldchange values of the treatment conditions
deseq_results %>% 
  select(log2FoldChange, MEAN_ID_TREATMENT) %>% 
  mutate(FoldChange = 2^log2FoldChange) %>% 
  ggplot() +
  geom_density(mapping = aes(x = log2FoldChange)) +
  facet_wrap(~MEAN_ID_TREATMENT) +
  theme_bw() + 
  labs(title = "Density plot of log2FoldChange values")

```

## Number of differentially expressed genes (DEGs)
```{r error=F,warning=F,message=F}
padj_threshold <- 0.05
log2FC_threshold <- log2(1.5)

deseq_results %>% 
  group_by(MEAN_ID_TREATMENT,.drop = F) %>% 
  filter(abs(log2FoldChange) > log2FC_threshold & padj < padj_threshold) %>% 
  dplyr::count(MEAN_ID_TREATMENT) %>% 
  ggplot(mapping = aes(x = reorder(MEAN_ID_TREATMENT, -n), y = n)) + 
  geom_bar(stat = "identity") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, size=6))
```

### Volcano plot
```{r}
padj_threshold <- 0.05
log2FC_threshold <- log2(1.5)

order <- c("HPPTEC_CSA_8hr_2", "HPPTEC_CSA_8hr_10", "HPPTEC_CSA_8hr_40","HPPTEC_CSA_24hr_2", "HPPTEC_CSA_24hr_10", "HPPTEC_CSA_24hr_40", "HPPTEC_CSA_72hr_2", "HPPTEC_CSA_72hr_10", "HPPTEC_CSA_72hr_40")

# We assign a status to every gene, either significant or not, based on the thresholds
red <- deseq_results %>%
  mutate(concentration = as.numeric(sub(".*_(\\d+)$", "\\1", MEAN_ID_TREATMENT))) %>%
  arrange(concentration) %>%
  drop_na() %>%
  mutate(MEAN_ID_TREATMENT = factor(MEAN_ID_TREATMENT, levels = order),  
         class = if_else(abs(log2FoldChange) > log2FC_threshold & padj < padj_threshold,
                         "significant",
                         "not significant"))


# We generate a scatter plot coloring the significant and not significant genes per treatment condition
plot <- ggplot(data = red, aes(x = log2FoldChange, y = -log10(padj), color = class)) + 
  facet_wrap(~MEAN_ID_TREATMENT, scales = "fixed") +  
  geom_point(size = 0.5) +
  theme_bw()

# We print the output to generate the plot
plot
```

## MA plot
```{r error=F,warning=F,message=F}
# Assign baseMean and log2FC thresholds
baseMean_threshold <- 2.5
log2FC_threshold <- 2.5
padj_threshold <- 0.05

order <- c("HPPTEC_CSA_8hr_2", "HPPTEC_CSA_8hr_10", "HPPTEC_CSA_8hr_40", 
           "HPPTEC_CSA_24hr_2", "HPPTEC_CSA_24hr_10", "HPPTEC_CSA_24hr_40", 
           "HPPTEC_CSA_72hr_2", "HPPTEC_CSA_72hr_10", "HPPTEC_CSA_72hr_40")
deseq_results$MEAN_ID_TREATMENT <- factor(deseq_results$MEAN_ID_TREATMENT, levels = order)


# We generate the plot and print the output
ggplot(data = deseq_results, aes(x = baseMean, y = log2FoldChange)) + 
  geom_point(size=0.5) +
  geom_point(data = deseq_results %>% filter(padj < padj_threshold), color = "red", size=0.5) +
  facet_wrap(~MEAN_ID_TREATMENT) +
  scale_x_continuous(limits = c(0,10)) +
  theme_bw() +
  labs(title = "MA plot with significant genes in red")
```

#### Principal component analysis on DESeq output using the log2FC values
```{r error=F,warning=F,message=F}

# We transpose prepare the data frame for pca analysis
log2fc_results <- deseq_results %>%
  select(gene_symbol, log2FoldChange, MEAN_ID_TREATMENT) %>%
  pivot_wider(names_from = MEAN_ID_TREATMENT, values_from = log2FoldChange)

# We print the genes with NA as log2FC result
print("NA genes dropped from PCA analysis")
log2fc_results[!!rowSums(is.na(log2fc_results)),]

# We further wrangle the data frame for pca analysis
pca_data <- log2fc_results %>% 
  drop_na() %>% 
  pivot_longer(cols = where(is.numeric), names_to = "MEAN_ID") %>% 
  pivot_wider(values_from = value, names_from = gene_symbol) %>%
  left_join(metadata, by="MEAN_ID")

# We perform pca analysis on numerical columns
pca_object = prcomp(pca_data %>% select(log2fc_results$gene_symbol), center = F, scale. = F)

# We print the output
  autoplot(object = pca_object, data = pca_data, colour = "TIMEPOINT", size = "CONCENTRATION") + 
    theme_bw()
```

# Create expression data
```{r}
expression_long = deseq_results %>% 
  select(sample_id = MEAN_ID_TREATMENT,
                gene_symbol,
                log2fc = log2FoldChange,
                pvalue,
                padj)


# add columns needed for TXG-MAPr
expression_long_TXG <- left_join(expression_long, metadata %>%
                                   dplyr::select("experiment" = "COMPOUND", "time" = "TIME", "conc" = "CONCENTRATION", "sample_id" = "MEAN_ID"),
                                 by = c("sample_id")) %>%
  dplyr::rename("gene_id" = "gene_symbol") %>%
  mutate(time = gsub("hr", "", time), # remove hr from time
         conc = gsub("uM", "", conc)) %>% # remove uM from conc
  select(everything(), -"sample_id")

```

# Save output
```{r}
write_rds(deseq_results, file.path(output_dir, paste0(gsub( "-", "", Sys.Date()), "_DESeq2_results_unformatted_human2.rds")))
write_delim(expression_long_TXG, file.path(output_dir, paste0(gsub( "-", "", Sys.Date()), "_expression_long_TXG_upload_human2.txt")))

```
